Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-05 paper/Intuition.tex
Introduction put back in. fix some links

\section{Proof of MSI protocol being preserving Store atomicity}
\label{safety}

In this section, we present the structure of the proof of Theorem
\fullref{storeAtomicity} for a system implementing the MSI protocol of
Figure~\ref{trans}. We reduce the whole system proof to that of a set of
invariants between any parent-child pair. These invariants in turn depend on
exactly two invariants. Identifying these two basic invariants is one of the
main contributions of the paper; they also hold for other protocols like MOSI
(discussed in Section \ref{sec:Refinements}).

>>>>

\section{Proof of MSI protocol being preserving Store atomicity}
\label{Sec:Safety}

In this section, we present the structure of the proof of Theorem
\fullref{storeAtomicity} for a system implementing the MSI protocol of
Figure~\ref{trans}. We reduce the whole system proof to that of a set of
invariants between any parent-child pair. These invariants in turn depend on
exactly two invariants. Identifying these two basic invariants is one of the
main contributions of the paper; they also hold for other protocols like MOSI
(discussed in Section~\ref{Sec:Refinements}).
